The Birth of a Galaxy: Primordial Metal Enrichment and Stellar Populations

### 2011-11-29 ApJ/ms.tex
Minor corrections in finish proofreading.

Building upon this idea of a lower metallicity floor, consider a
pre-galactic halo that has hosted a Pop III star, producing a SN.  The
majority of the gas is ejected into the IGM and re-accretes after
$\sim 10-50$ Myr \citep{Johnson07, Wise08_Gal}.  What happens if the
metallicity is not greater than the critical metallicity?  Massive Pop
III stars would form again in this halo; however, enriching the
surrounding IGM with Pop III SNe and ejecting material becomes more
difficult in halos with $M \gsim 10^7 \Ms$ \citep{Whalen08_SN}.  Thus
it is more likely for these subsequent Pop III stars to retain more of
its gas during star formation episodes and self-enrich its host halo
and less of the IGM.  This would accelerate the transition from Pop
III to II in more massive halos.

Using our result of the metallicity floor, we conclude that it only
takes one, at most two, SNe from Pop III stars in the halo progenitors
to complete the transition to Population II \citep{Frebel10}.
However, this does not prohibit more than two instances of Pop III
star formation in halo from happening because the stars can produce
BHs with little or no metal ejecta, keeping the surrounding
environment pristine.  Although we find that Pop III SNe create a
floor of $10^{-4} - 10^{-3} \zsun$, gas with $Z/\zsun < 10^{-4}$ can
still exists in nearby halos, where the metal-rich SN ejecta mix
slowly into dense cores as the blastwave overtakes it \citep{Cen08}.
These environments may be the host of true extremely metal-poor star
formation, such as the recently discovered halo star with all detected
metals below $10^{-4.2} \zsun$ \citep{Caffau11}.

>>>>

Building upon this idea of a lower metallicity floor, consider a
pre-galactic halo that has hosted a Pop III star, producing a SN.  The
majority of the gas is ejected into the IGM and re-accretes after
$\sim 10-50$ Myr \citep{Johnson07, Wise08_Gal}.  What happens if the
metallicity is not greater than the critical metallicity?  Massive Pop
III stars would form again in this halo; however, enriching the
surrounding IGM with Pop III SNe and ejecting material becomes more
difficult in halos with $M \gsim 10^7 \Ms$ \citep{Whalen08_SN}.  Thus
it is more likely for these halos to retain more of its gas during
star formation episodes and self-enrich its host halo and less of the
IGM.  This would accelerate the transition from Pop III to II in more
massive halos.

We conclude that it only takes one, at most two, SNe from Pop III
stars in the halo progenitors to complete the transition to Population
II \citep{Frebel10}.  However, this does not prohibit more than two
instances of Pop III star formation in halo from happening because the
stars can produce BHs with little or no metal ejecta, keeping the
surrounding environment pristine.  Even though we find that Pop III
SNe create a floor of $\sim 10^{-3} \zsun$, gas with lower
metallicities can still exists in nearby halos, where the metal-rich
SN ejecta will mix slowly into dense cores as the blastwave overtakes
them \citep{Cen08}.  These environments may be the host of true
extremely metal-poor star formation, such as the recently discovered
halo star with all detected metals below $10^{-4.2} \zsun$
\citep{Caffau11}.
